Wood density and the growth-dependent & independent mortality

### 2015-04-08 ms.Rmd
Added example rstan code to implement kfold cross validation

##Model Code

>>>>

## K-fold Cross validation example excerp from [Vehtari & Gelman 2014](http://www.stat.columbia.edu/~gelman/research/unpublished/waic_stan.pdf)

To implement K-fold cross-validation in Stan we need to repeatedly fit the model to one subset of the data and use it to predict the held-out set. The way we recommend setting this up is to do the partitioning in R (or Python, or whatever data-processing environment is being used) and then pass the training data and held-out data to Stan in two pieces.
With linear regression, for example, we start with the Stan model on page 4, passing in the training data as N, y, X and the held-out set as N holdout, y holdout, X holdout, with the data block augmented accordingly. We then keep the data block and model as is, and just alter the generated quantities block to operate on the held-out data. The code looks like this:

```{r eval=FALSE}
􏰋
￼￼￼data { int N;
  int J;
vector[N] y;
matrix[N,J] X;
int N_holdout;
vector[N_holdout] y_holdout;
matrix[N_holdout,J] X_holdout;
}
  parameters {
    vector[J] b;
real<lower=0> sigma;
  }
  model {
    y ~ normal(X*b, sigma);
increment_log_prob(-log(sigma));
  }
  generated quantities {
    vector[N_holdout] log_lik;
for (n in 1:N_holdout){
  // data model
// log prior for p(sigma) propto 1/sigma
log_lik[n] <- normal_log(y_holdout[n], X_holdout[n]*b, sigma);
9
} }
